Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-12 providence/sections/appendix.tex

\begin{proof}
\label{pf:efficiency_proof}
Let $[n_1, \ldots, n_j]$ be a round schedule, and assume that an EoR \BRAVO audit stops in round $j$, after observing $k_1, \ldots, k_j$ ballots for the announced winner in each round respectively.
That is, the EoR \BRAVO stopping condition is true:
$$\sigma(k_j,p_a,p_0,n_j) \ge \frac{1}{\alpha}.$$
To see the \Providence stopping condition is fulfilled, we rewrite as 
%$$\frac{1}{\alpha} \le \sigma(k_j,p_a,p_0,n_j)=\sigma(k_j,p_a,p_0,n_j)$$

@@

Where inequality $(*)$ follows from \cite[Theorem 6]{athena}. Note that we apply this result on $\tau_j$ for just $j=1$.
%Where inequality $(*)$ follows from Lemma~\ref{lemma:frac_sums_increasing}.
%the well-known property that if $a_i/b_i$ (for $a_i, b_i > 0$) is monotonicly increasing then
%(\sum_{i} a_i)/(\sum_{i} b_i)$ is also monotonicly increasing.

>>>>

\begin{proof}
Let $[n_1, \ldots, n_j]$ be a round schedule, and assume that an EoR \BRAVO audit stops in round $j$, after observing $k_1, \ldots, k_j$ ballots for the announced winner in each round respectively.
That is, the EoR \BRAVO stopping condition is true:
$$\sigma(k_j,p_a,p_0,n_j) \ge \frac{1}{\alpha}.$$
To see the \Providence stopping condition is fulfilled, we rewrite as 
%$$\frac{1}{\alpha} \le \sigma(k_j,p_a,p_0,n_j)=\sigma(k_j,p_a,p_0,n_j)$$

@@

Where inequality $(*)$ follows from \cite[Theorem 6]{arxiv_athena}. Note that we apply this result on $\tau_j$ for just $j=1$.
%Where inequality $(*)$ follows from Lemma~\ref{lemma:frac_sums_increasing}.
%the well-known property that if $a_i/b_i$ (for $a_i, b_i > 0$) is monotonicly increasing then
%(\sum_{i} a_i)/(\sum_{i} b_i)$ is also monotonicly increasing.
